A Modular Framework for Developing, Deploying, and Evaluating Game-Theoretic Strategy Design Exercises

### 2018-05-07 paper.tex
Factor out problem background

\newpage
\section*{Introduction}
My work builds upon existing programming-based game theory exercises assigned in an existing Princeton course, COS 445 ``Economics and Computing''.
The intention of these strategy design exercises is to teach students how to use game theory to analyze a real world situation and work rationally within a healthy incentive structure where students do not try to hurt each others’ performance.
Each past offering of the course has rebuilt these assignments, and all associated instructor tooling, from scratch, resulting in unnecessarily high allocation of instructor time to grading.
Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{registrar data here}\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}
In order to eliminate unnecessary annual replication of previous coursework development, improve course performance at scale, and improve the course experience for students, I developed an extensible framework to improve these strategy design exercises.

Four Princeton University departments offer courses in game theory: Economics, Politics, Mathematics, and Computer Science.
While all of these courses teach the core concepts of game theory, each also connects this core to relevant examples and topics in its department.
For instance, the Computer Science department's ``Economics and Computing'' places emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
The course focuses on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.\footnote{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
It is also represented in the design of the problem sets, which, in addition to traditional proof-based exercises, contain programming-based exercises which connect course topics to prerequisite computer science skills.
These programming-based exercises take a common form.

@@

%TODO: move the above into the body / approach and the above as the introduction
The goals of this project are to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition.
This was accomplished by designing a reusable framework which embodies the commonality between strategy design exercises, allowing instructors to create new exercises while changing only the necessary, assignment-specific details, and to develop advanced automated grading tools than previously existed for the course.
Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.

@@

%the "programming assignments" aren't really about your ability to code. They are about placing the theoretical results from the course in context. They create a scenario in which mastery of theoretical results from the course content is demonstrated by making and justifying real-world decisions.

>>>>

\newpage
\section*{Introduction}
My work builds upon existing programming-based game theory exercises assigned in an existing Princeton course, COS 445 ``Economics and Computing''.
The intention of these strategy design exercises is to teach students how to use game theory to analyze a real world situation and work rationally within a healthy incentive structure where students do not try to hurt each others’ performance.
Each past offering of the course has rebuilt these assignments, and all associated instructor tooling, from scratch, resulting in unnecessarily high allocation of instructor time to grading.
Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{registrar data here}\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}

The goals of this project are to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition.
This was accomplished by designing a modular, extensible, and reusable framework which embodies the commonality between strategy design exercises, allowing instructors to create new exercises while changing only the necessary, assignment-specific details, and to develop advanced automated grading tools than previously existed for the course.
Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.

\section*{Problem Background}
Four Princeton University departments offer courses in game theory: Economics, Politics, Mathematics, and Computer Science.
While all of these courses teach the core concepts of game theory, each also connects this core to relevant examples and topics in its department.
For instance, the Computer Science department's ``Economics and Computing'' places emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
The course focuses on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.\footnote{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
It is also represented in the design of the problem sets, which, in addition to traditional proof-based exercises, contain programming-based exercises which connect course topics to prerequisite computer science skills.
These programming-based exercises take a common form.

@@

% the "programming assignments" aren't really about your ability to code. They are about placing the theoretical results from the course in context. They create a scenario in which mastery of theoretical results from the course content is demonstrated by making and justifying real-world decisions.

@@
